### 2018-02-06 usenix18/pipe.tex
some formatting changed in the eval sec.
code partitioning example

Thus, given a decomposition of $\prog$ into
$\prog_1\seq\prog_2\seq\dots\seq\prog_k$, we can use the construction
above to generate programs $\progn_1,\progn_2,\ldots,\progn_k$, that
can be sequentially executed, using the unmodified underlying \mpc
backend. The following theorem states the correctness and security of
the scheme.

@@

\noindent {\em Proof.} Let $\progn_1, \ldots, \progn_k$ be the
sequence of programs as defined above corresponding to the
decomposition $\prog = \prog_1||\prog_2||\ldots||\prog_k$.  For every
$1\leq i\leq k$, let $\prot_i$ be the \mpc protocol output by our
framework for $\progn_i$. Our construction for programs $\progn_i$
ensures that if $\prog$ is well-typed, then for each $1\leq i \leq k$,
$\progn_i$ is well-typed. Then, by \theoremref{security}, $\prot_i$,
the \mpc protocol that evaluates the circuit generated by $\progn_i$,
securely realizes $\progn_i$. That is, for every $1\leq i \leq k-1$,
the protocol $\prot_i$ provides observations $r_i$ to Alice and $o_i$
to Bob. And, protocol $\prot_k$ provides observation $z$ to both Alice
and Bob. Finally, since $r_i$ and $o_i$ ($1\leq i\leq k-1$) are
individually uniformly random (in $(\mathbb{Z},+)$, outputs received
by the adversary can be simulated given the final output $z$.

@@

\subsubsection*{Managing circuit sizes using partitioning}
We use partitioning for programs that require large
circuits. Specifically, the programmer decomposes the program
$\prog$ into a sequence of small programs
$\prog_1\seq\dots\seq\prog_k$ manually. And then, \tool generates
sequence of programs $\progn_1,\dots\progn_k$ automatically. We then
compile and execute the $k$ programs
$\progn_1,\progn_2,\ldots,\progn_k$ sequentially, freeing up memory
usage after execution of each $\progn_i$.
Automating the manual decomposition step requires an analysis that can 
statically estimate the resource usage of a \tool program and we leave
the construction of such an analysis as future work.

>>>>

Thus, given a decomposition of $\prog$ into
$\prog_1\seq\prog_2\seq\dots\seq\prog_k$, we can use the construction
above to generate programs $\progn_1,\progn_2,\ldots,\progn_k$, that
can be sequentially executed, using the unmodified underlying \mpc
backend.

\paragraph{Example of code partitioning.} We now illustrate code partitioning through an example. Consider the functionality in Figure \ref{fig:largecode}. This is a functionality that takes as input two vectors $w$ and $v$ from Alice and two vectors $x$ and $y$ from Bob. It computes two inner products $w^Tx$ and $v^Ty$, compares the first value with the second and returns a boolean value (which is $1$ if $w^Tx>v^Ty$ and $0$ otherwise) to Bob. Now, if we wish to partition this functionality using secure code partitioning, one possible split is as follows into the following three programs\footnote{All arithmetic is over an appropriate ring in the following discussion.}. Partition $1$ (Figure \ref{fig:codepartitioning1}) computes $w^Tx$ and ``secret shares'' the output of this computation between Alice and Bob (Alice's share is $r_1$, a random value, and Bob's share is $o_1 = w^Tx+r_1$). Next, partition $2$ (Figure \ref{fig:codepartitioning2}) computes $v^Ty$ and once again provides Alice with $r_2$ and Bob with $o_2 = v^Ty+r_2$. Finally, partition $3$ (Figure \ref{fig:codepartitioning3}) compares $o_1-r_1$ with $o_2-r_2$ and provides the output to Bob. It is easy to see that the size of the programs $1, 2$ and $3$ (and their corresponding circuits output by the \tool compiler) are smaller than the program in Figure \ref{fig:largecode} and its corresponding circuit, and in particular, smaller than the state that must be maintained between the programs.

\begin{figure}
\begin{lstlisting}[language=C,mathescape=true]
$\mathtt{
uint\;w[30] = input1();\;\;uint\;v[30] = input1();
}$
$\mathtt{
uint\;x[30] = input2();\;\;uint\; y[30] = input2();
}$
$\mathtt{
uint\;acc1 = 0;\;\;uint\;acc2 =0;
}$
$\mathtt{
for\;i\;in\;[0:30]\;
}$
$\mathtt{\{acc1\;=\;acc1\;+\;(w[i]\;\times\;x[i]);\;
}$
$\mathtt{\;\;acc2\;=\;acc2\;+\;(v[i]\;\times\;y[i]);\}
}$
$\mathtt{
output2((acc1 > acc2)\;?\;1\;:\;0)\;\textbf{{\color{blue}//only to party 2}}
}$
\end{lstlisting}
\caption{\tool code for $w^Tx > v^Ty$}
\label{fig:largecode}
\end{figure}

\begin{figure}
\begin{lstlisting}[language=C,mathescape=true]
$\mathtt{
uint\;w[30] = input1();\;\;uint\;r1 = input1();
}$
$\mathtt{
uint\;x[30] = input2();
}$
$\mathtt{
uint\;acc1 = 0;
}$
$\mathtt{
for\;i\;in\;[0:30]\;\{acc1\;=\;acc1\;+\;(w[i]\;\times\;x[i]);\}
}$
$\mathtt{
uint\;o1 = acc1+r1;
}$
$\mathtt{
output2(o1)\;\textbf{{\color{blue}//acc1 is ``secret shared''}}
}$
\end{lstlisting}
\caption{Partition 1: Code for $o_1 = w^Tx+r_1$}
\label{fig:codepartitioning1}
\end{figure}

\begin{figure}
\begin{lstlisting}[language=C,mathescape=true]
$\mathtt{
uint\;v[30] = input1();\;\;uint\;r2 = input1();
}$
$\mathtt{
uint\;y[30] = input2();
}$
$\mathtt{
uint\;acc2 =0;
}$
$\mathtt{
for\;i\;in\;[0:30]\;\{acc2\;=\;acc2\;+\;(v[i]\;\times\;y[i]);\;\}
}$
$\mathtt{
uint\;o2 =acc2+r2;
}$
$\mathtt{
output2(o2)\;\textbf{{\color{blue}//acc2 is ``secret shared''}}
}$
\end{lstlisting}
\caption{Partition 2: Code for $o_2 = v^Ty+r_2$}
\label{fig:codepartitioning2}
\end{figure}

\begin{figure}
\begin{lstlisting}[language=C,mathescape=true]
$\mathtt{
uint\;r1 = input1();\;\;uint\;r2 = input1();
}$
$\mathtt{
uint\;o1 = input2();\;\;uint\; o2 = input2();
}$
$\mathtt{
uint\;acc3 = o1-r1;\;\;uint\;acc4 =o2-r2;
}$
$\mathtt{
output2((acc3 > acc4)\;?\;1\;:\;0)\;\textbf{{\color{blue}//only to party 2}}
}$
\end{lstlisting}
\caption{Partition 3: Code for $(o_1-r_1)>(o_2-r_2)$}
\label{fig:codepartitioning3}
\end{figure}

\paragraph{Security.} The following theorem states the correctness and security of
code partitioning.

@@

\noindent {\em Proof.} Let $\progn_1, \ldots, \progn_k$ be the
sequence of programs as defined above corresponding to the
decomposition $\prog = \prog_1||\prog_2||\ldots||\prog_k$.  For every
$1\leq i\leq k$, let $\prot_i$ be the \mpc protocol output by our
framework for $\progn_i$. Our construction for programs $\progn_i$
ensures that if $\prog$ is well-typed, then for each $1\leq i \leq k$,
$\progn_i$ is well-typed. By \theoremref{security}, $\prot_i$,
the \mpc protocol that evaluates the circuit generated by $\progn_i$,
securely realizes $\progn_i$. That is, for every $1\leq i \leq k-1$,
the $\prot_i$ provides observations $r_i$ to Alice and $o_i$
to Bob. Protocol $\prot_k$ provides observation $z$ to both Alice
and Bob. Finally, since $r_i$ and $o_i$ ($1\leq i\leq k-1$) are
individually uniformly random (in $(\mathbb{Z},+)$, outputs received
by the adversary can be simulated given the final output $z$.

@@

\paragraph{Managing circuit sizes using partitioning.}
We use partitioning for programs that require large
circuits. Specifically, the programmer decomposes the program
$\prog$ into a sequence of small programs
$\prog_1\seq\dots\seq\prog_k$ manually. And then, \tool generates
sequence of programs $\progn_1,\dots\progn_k$ automatically. We then
compile and execute the $k$ programs
$\progn_1,\progn_2,\ldots,\progn_k$ sequentially, freeing up memory
usage after execution of each $\progn_i$.
Automating the manual decomposition step requires an analysis that can 
statically estimate the resource usage of a \tool program and we leave
the construction of such an analysis as future work. \nc{Are we trying to say here which part is manual and which part is automatic? This paragraph is a bit unclear to me.}
